This internship report describes the development of an automated solution for Veeries, an organization operating in the agribusiness sector that offers market analysis and commodity flow products. The core problem addressed was the severe operational bottleneck in the data ingestion of PDF reports from two confidential external sources. This extraction was performed strictly manually by the analyst team, consuming about three hours per batch and presenting a high susceptibility to human and structural failures. To solve this technological and business challenge, an event-driven data pipeline was designed and implemented based on the Medallion Architecture (composed of progressive Bronze, Silver, and Gold layers) and built in Python, supported by Pandas and Pandera libraries. The workflow automated the raw extraction from the unstructured format and implemented strict Data Contracts (schemas) for mathematical and semantic validations, in addition to adopting an architectural strategy of immediate interruption in case of structural anomalies (fail-fast). As a direct result of the deployment, the processing time of a report batch was reduced from hours to an interval of 2 to 5 seconds. The automated pipeline transferred the technical responsibility entirely to the developers' team, freed market analysts from manual transcription tasks, and provided high governance, traceability, and resilience to the organization's database. The system proved capable of intercepting and blocking publication errors from the issuing sources themselves before they reached the analytical and decision-making tools of the board.

\vspace{\onelineskip}
\noindent
\textbf{Key-words:} Data Engineering. Medallion Architecture. Data Pipeline. Data Quality. Automation.